BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-11 tex/3-algorithms.tex
Update 3-algorithms.tex

% comments
Comments are usually available in separate web feeds, one per blog post. Similarly to blog feeds, comment feeds have a limited number of entries, and when the number of comments on a blog post exceeds this limit, comments have to be extracted from the post web page. To do so we use the following \code{ScoreFunction}:
\begin{itemize}
  \item Rules returning less HTML nodes than the number of comments on the feed are filtered out with a zero score,
  \item Remaining rule scores are computed with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ has weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
\end{itemize}
Our crawler executes this algorithm on each post with an overflow on its comment feed, thus supporting blogs with multiple commenting engines. The comment content is extracted first, allowing us to narrow down the initial filtering by fixing a target number of comments.

% rush some time complexity analysis
Regarding time complexity, computing the \emph{tree distance} of each node of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affect the asymptotic computational complexity. Computing scores or comment extraction rules requires a more expensive algorithm. However, this is compensated by the fact that the proportion of candidates left, after filtering out rules not returning enough results, is very low in practice. Analogous reformulations to the one done with \autoref{linearAlgo} can be straightforwardly applied on each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.

>>>>

% comments
Comments are usually available in separate web feeds, one per blog post. Similarly to blog feeds, comment feeds have a limited number of entries, and when the number of comments on a blog post exceeds this limit, comments have to be extracted from the post web page. To do so we use the following \code{ScoreFunction}:
\begin{itemize}
  \item Rules returning less HTML nodes than the number of comments on the feed are filtered out with a zero score,
  \item The scores of the remaining rules are computed with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ has weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
\end{itemize}
Our crawler executes this algorithm on each post with an overflow on its comment feed, thus supporting blogs with multiple commenting engines. The comment content is extracted first, allowing us to narrow down the initial filtering by fixing a target number of comments.

% rush some time complexity analysis
Regarding time complexity, computing the \emph{tree distance} of each node of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affect the asymptotic computational complexity. Computing scores of comment extraction rules requires a more expensive algorithm. However, this is compensated by the fact that the proportion of candidates left, after filtering out rules not returning enough results, is very low in practice. Analogous reformulations to the one done with \autoref{linearAlgo} can be straightforwardly applied on each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.
